Draft Exploration

### 2020-04-18 draft_exploration.Rmd
removed NA war observations when summarizing war in war_joined

# grouping war data by player and summing career games played and war

war_joined <- war %>%
  group_by(mlb_ID) %>%
  summarize(g = sum(G),
            war = sum(as.numeric(war)))

>>>>

# grouping war data by player and summing career games played and war
# NOTE: I filtered out NA war observations so the summarized war would not also
# be NA due to a single NA observation of war

war_joined <- war %>%
  group_by(mlb_ID) %>%
  filter(!is.na(war)) %>%
  summarize(g = sum(G),
            war = sum(as.numeric(war)))
